An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2014-11-04 mixedwindow.tex

Assumption~\ref{a3} describes the DGP. The weak dependence and moment
conditions are standard. These assumptions are slightly weaker than
similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
because we make use of more recent developments in limit theory, in
particular the CLT for Near-Epoch Dependent (NED) processes proven by
\cite{Jon:97}.

\begin{asmp}\label{a3}%
  The series $y_t$, $x_t$, and $z_t$ are $L_2$-NED of size
  $-(r-1)/(r-2)$ for $r > 2$ on either a strong mixing process of size
  $-r/(r-2)$ or a uniform mixing process of size
  $-r/(2r-2)$. Moreover, $y_t$, $x_t$, and $\yh_{j,t}$, $j =
  1,\dots,J$, have uniformly bounded $2 r$ moments.
\end{asmp}

The requirement that the alternative forecasts satisfy a moment
condition, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The functions $\psi_j$ that generate these
forecasts is essentially unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a CLT from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.

>>>>

Assumption~\ref{a3} describes the \dgp. The weak dependence and moment
conditions are standard. These assumptions are slightly weaker than
similar assumptions in \citet{Wes:96} and \citet{Mcc:00}, but only
because we make use of more recent developments in limit theory, in
particular the \clt\ for Near-Epoch Dependent (\ned) processes proven by
\cite{Jon:97}.

\begin{asmp}\label{a3}%
  The series $y_t$, $x_t$, and $z_t$ are $L_2$-\ned\ of size
  $-(r-1)/(r-2)$ for $r > 2$ on either a strong mixing process of size
  $-r/(r-2)$ or a uniform mixing process of size
  $-r/(2r-2)$. Moreover, $y_t$, $x_t$, and $\yh_{j,t}$, $j =
  1,\dots,J$, have uniformly bounded $2 r$ moments.
\end{asmp}

The requirement that the alternative forecasts satisfy a moment
condition, rather than the underlying predictors $z_t$, is somewhat
unappealing but necessary. The functions $\psi_j$ that generate these
forecasts is essentially unrestricted, so even well-behaved predictors
could produce arbitrarily badly-behaved forecasts. For example, if
\begin{equation*}
  z_t \sim \iid~\bernoulli(1/2),
\end{equation*}
setting $\psi_1(y_t, z_t) = 1/z_t$ would prevent a \clt\ from holding
since the forecast equals positive infinity with probability $1/2$. It
is easy to construct less obvious examples of problematic functions as
well. Assumption~\ref{a3} implicitly rules out these functional forms
by imposing moment conditions on the alternative models' forecasts.
